Probabilistic Forecasts in Hierarchical~Time~Series

### 2018-06-29 ProbabilisticCoherence.tex
New tables of results (with seed saved)

\begin{table}
  \caption{Comparison of incoherent forecasts using bottom-level series. The ``Skill score'' columns give the percentage skill score with reference to the bottom-up forecasting method. Entries in these columns show the percentage increase of score for different reconciliation methods relative to the bottom-up method.}\label{table:3}
  \centering\small
  \begin{tabular}{@{}lSSSSSS@{}}
    \toprule
    Forecasting &
    \multicolumn{2}{c}{\text{Energy score}} &
    \multicolumn{2}{c}{\text{Log score}} &
    \multicolumn{2}{c}{\text{Variogram score}} \\
    \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(l){6-7}
    method &
    \text{Mean score} & \text{Skill score} &
    \text{Mean score} & \text{Skill score} &
    \text{Mean score} & \text{Skill score}\\
    \midrule
    MinT(Shrink) &  7.47 &  10.11 &  11.34 &     6.44 & 3.05 &   4.69 \\
    MinT(Sample) &  7.47 &  10.11 &  11.33 &     6.52 & 3.05 &   4.69 \\
    MinT(WLS)    &  7.91 &   4.81 &  12.64 &    -4.29 & 3.23 &  -0.94 \\
    OLS          & 10.14 & -22.02 & 135.13 & -1014.93 & 4.60 & -43.75 \\
    Bottom-up    &  8.31 &        &  12.12 &          & 3.20 &        \\
    \bottomrule
  \end{tabular}
\end{table}

\begin{table}
  \caption{Comparison of incoherent vs coherent forecasts for the aggregate series using Skill scores. The ``Incoherent'' row shows the average scores for incoherent forecasts. Each entry above this row represents the percentage skill score with reference to the incoherent forecasts. Entries show the percentage increase in score for different forecasting methods relative to the incoherent forecasts.}\label{table:4}
  \centering\small
  \begin{tabular}{@{}lSSSSSS@{}}
    \toprule
    Forecasting &
    \multicolumn{2}{c}{\text{Total}} &
    \multicolumn{2}{c}{\text{Series - A}} &
    \multicolumn{2}{c}{\text{Series - B}} \\
    \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(l){6-7}
    method      &  CRPS   & LogS    & CRPS   & LogS     & CRPS   & LogS     \\
    \midrule
    MinT(Shrink) & 1.12   & 0.34    & 10.07  & 2.93     & 5.41   & 1.52     \\
    MinT(Sample) & 1.12   & 0.34    & 10.07  & 2.93     & 5.41   & 1.52     \\
    MinT(WLS)    & -2.61  & -2.02   & 5.28   & -4.40    & 2.70   & -4.24    \\
    OLS          & -38.06 & -698.99 & -24.70 & -1368.33 & -24.86 & -1159.09 \\
    Bottom-up    & -89.55 & -21.83  & -8.87  & -2.35    & -9.46  & -2.73    \\
    \midrule
    \textit{Incoherent} & $\mathbi{2.68}$ & $\mathbi{2.97}$ & $\mathbi{4.17}$ & $\mathbi{3.41}$ & $\mathbi{3.70}$ & $\mathbi{3.30}$ \\
    \bottomrule
  \end{tabular}
\end{table}

\begin{table}
  \caption{Comparison of incoherent vs coherent forecasts for the individual bottom-level series using Skill scores.}\label{table:5}
  \centering\tabcolsep=0.08cm\small
  \begin{tabular}{@{}lSSSSSSSS@{}}
    \toprule
    Forecasting &
    \multicolumn{2}{c}{\text{Series - AA}} &
    \multicolumn{2}{c}{\text{Series - AB}} &
    \multicolumn{2}{c}{\text{Series - BA}} &
    \multicolumn{2}{c}{\text{Series - BB}} \\
    \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(l){8-9}
    method       & CRPS   & LogS    & CRPS   & LogS    & CRPS   & LogS    & CRPS   & LogS \\
    \midrule
    MinT(Shrink) & 8.71   & 2.71    & 10.57  & 3.04    & 5.95   & 1.86    & 7.91   & 2.46 \\
    MinT(Sample) & 8.71   & 2.71    & 10.57  & 3.04    & 5.95   & 1.86    & 8.19   & 2.46 \\
    MinT(WLS)    & 5.54   & 0.30    & 5.96   & 0.30    & 2.43   & -0.62   & 5.08   & 0.62 \\
    OLS          & -22.43 & -931.63 & -22.49 & -886.32 & -26.01 & -834.67 & -23.45 & -812.92 \\
    \midrule
    \textit{Incoherent} & $\mathbi{3.79}$ & $\mathbi{3.32}$ & $\mathbi{3.69}$ & $\mathbi{3.29}$ & $\mathbi{3.46}$ & $\mathbi{3.23}$ & $\mathbi{3.54}$ & $\mathbi{3.25}$ \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\begin{table}
	\caption{Comparison of coherent forecasts. ``Energy score'' and ``Variogram score'' columns give scores based on the joint forecast distribution of whole hierarchy. ``Log score'' column gives the log scores of the joint forecast distribution of bottom level. ``Skill score'' columns give the percentage skill score with reference to the bottom-up method. Entries in these columns show the percentage increase of score for different reconciliation methods relative to the bottom-up method. }\label{table:3}

	\centering\small
	\begin{tabular}{@{}lSSSSSS@{}}
		\toprule
		Forecasting &
		\multicolumn{2}{c}{\text{Energy score}} &
		\multicolumn{2}{c}{\text{Variogram score}} &
		\multicolumn{2}{c}{\text{Log score}} \\
		\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(l){6-7}
		method &
		\text{Mean score} & \text{Skill score \%} &
		\text{Mean score} & \text{Skill score \%} &
		\text{Mean score} & \text{Skill score \%}\\
		\midrule
		MinT(Shrink) &  10.03 & 18.79  & 8.44  & 8.46 & 11.30 &  6.22 \\
		MinT(Sample) &  10.01 & 18.95  & 8.41  & 8.79 & 11.29 &  6.31 \\
		MinT(WLS)    &  10.53 & 14.74  & 9.02  & 2.17 & 12.61 & -4.65 \\
		OLS          &  10.53 & 14.74  & 8.86  & 3.09 & 11.54 &  4.23\\
		Bottom-up    &  12.35 &    	   & 9.22  &      & 12.05 &  \\
		Incoherent	 &  11.12 &   	   & 9.53  &      &       &  \\
		\bottomrule
	\end{tabular}
\end{table}

\begin{table}
	\caption{Comparison of incoherent vs coherent forecasts based on the univariate forecast distribution of aggregate series. The ``Incoherent'' row shows the average scores for incoherent forecasts. Each entry above this row represents the percentage skill score with reference to the incoherent forecasts. These entries show the percentage increase in score for different forecasting methods relative to the incoherent forecasts.}\label{table:4}
	\centering\small
	\begin{tabular}{@{}lSSSSSS@{}}
		\toprule
		Forecasting &
		\multicolumn{2}{c}{\text{Total}} &
		\multicolumn{2}{c}{\text{Series - A}} &
		\multicolumn{2}{c}{\text{Series - B}} \\
		\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(l){6-7}
		method      &  CRPS   & LogS    & CRPS   & LogS     & CRPS   & LogS     \\
		\midrule
		MinT(Shrink) &   0.74  &   0.00   & 10.49   &  3.24  &  9.16  &  2.73    \\
		MinT(Sample) &   0.74  &   0.00   & 10.49   &  3.24  &  9.16  &  2.73    \\
		MinT(WLS)    &  -2.96  &  -2.36   &  6.10   & -4.12  &  5.66  & -3.03    \\
		OLS          &  -9.26  &  -3.36   &  7.07   &  2.06  &  7.01  &  1.82    \\
		Bottom-up    & -91.48  & -22.22   & -8.05   & -2.06  & -6.20  & -1.82    \\
		\midrule
		\textit{Incoherent} & $\mathbi{2.70}$ & $\mathbi{2.97}$ & $\mathbi{4.10}$ & $\mathbi{3.40}$ & $\mathbi{3.71}$ & $\mathbi{3.30}$ \\
		\bottomrule
	\end{tabular}
\end{table}

\begin{table}
	\caption{Comparison of incoherent vs coherent forecasts based univariate forecast distribution of bottom-level series. The ``Incoherent'' row shows the average scores for incoherent forecasts.}\label{table:5}
	\centering\tabcolsep=0.08cm\small
	\begin{tabular}{@{}lSSSSSSSS@{}}
		\toprule
		Forecasting &
		\multicolumn{2}{c}{\text{Series - AA}} &
		\multicolumn{2}{c}{\text{Series - AB}} &
		\multicolumn{2}{c}{\text{Series - BA}} &
		\multicolumn{2}{c}{\text{Series - BB}} \\
		\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(l){8-9}
		method       & CRPS   & LogS    & CRPS   & LogS    & CRPS   & LogS    & CRPS   & LogS \\
		\midrule
		MinT(Shrink) &  7.61  &  2.43  &  10.82  &  3.02  &  5.93  &  1.86  &  7.76  & 2.47  \\
		MinT(Sample) &  7.88  &  2.43  &  11.08  &  3.02  &  6.20  &  1.86  &  8.05  & 2.47  \\
		MinT(WLS)    &  3.53  &  0.00  &   6.33  &  0.60  &  2.43  & -0.62  &  4.89  & 0.62  \\
		OLS          &  2.99  &  0.91  &   5.28  &  1.51  &  2.90  &  0.62  &  4.31  & 1.23  \\
		\midrule
		\textit{Incoherent} & $\mathbi{3.68}$ & $\mathbi{3.29}$ & $\mathbi{3.79}$ & $\mathbi{3.31}$ & $\mathbi{3.45}$ & $\mathbi{3.22}$ & $\mathbi{3.48}$ & $\mathbi{3.24}$ \\
		\bottomrule
	\end{tabular}
\end{table}
